### 2014-04-17 paper_skeleton.tex
focusing on accuracy of 2d process now that i think theyre the same

We find that the two-dimensional decision is less accurate than the one-dimensional decision.  That is, for a given expected time to reach a decision, the two-dimensional decision will reach the correct decision with a lower probability (Figure \ref{1dv2d}).  The difference in probability is very low when memory is perfect (i.e. $\ell=0$).  However, at higher leak rates the difference becomes more pronounced.  Further, when the strength of the input ($d$) is lower, the difference becomes greater.  Thus, as the decision becomes harder because either memory decreases or the true state of the world becomes harder to detect, the advantage of the one-dimensional system increases.

Without any prior knowledge of the probabilities of the state of the visual stimulus, it is reasonable to assume that the thresholds for deciding for each direction are symmetric.  On the other hand, in the social system, the thresholds are chosen by two competing animals and there is less reason to assume that their thresholds are the same.  The accuracy in a given amount of time depends on the ratio of the two thresholds and is improved when the weaker animal's threshold is lower than the stronger animal's threshold (Figure \ref{2dthresh}).

@@

\begin{figure}
\includegraphics[width=\textwidth]{1d_v_2d_symmetric.pdf}
\caption{\label{1dv2d} A two-dimensional decision process, in which the decision is made when either of the variables reaches a threshold, is less accurate than a one-dimensional decision process, in which the decision is made when the difference between the variables reaches a threshold.  In each panel, the expected time to reach a decision is on the x-axis and the probability of reaching the correct decision in that amount of time is on the y-axis.  Red curves represent a one-dimensional decision and red curves represent a two-dimensional decision.  Stronger values of the input are represented in higher darker curves.  In the left panel, there is no leak.  In the right panel, leak rate is set to $\ell=.5$.  Other parameters are set as follows:}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{2d_flexible_thresholds.pdf}
\caption{\label{2dthresh} When the two thresholds in the two-dimensional case are allowed to vary freely, the decision process can be arbitrarily accurate in a given amount of time, depending on how much lower the weaker animal's threshold is than the stronger animal's threshold.  The expected time to reach a decision is on the x-axis and the probability of reaching the correct decision in that amount of time is on the y-axis.  The curve depends on the ratio of the weaker animal's threshold to the stronger animal's threshold ($\rho$).  Lower ratios are represented in higher darker curves.}
\end{figure}

>>>>

We find that the two-dimensional decision is as accurate as the one-dimensional decision.  That is, for a given expected time to reach a decision, the two-dimensional decision will reach the correct decision with the same probability.  Accuracy decreases as leak rates ($\ell$) become higher, but increases when the strength of the input ($d$) is higher (Figure \ref{2dacc}).

Without any prior knowledge of the probabilities of the state of the visual stimulus, it is reasonable to assume that the thresholds for deciding for each direction are symmetric.  On the other hand, in the social system, the thresholds are chosen by two competing animals and there is less reason to assume that their thresholds are the same.  The accuracy in a given amount of time depends on the ratio of the two thresholds and is improved when the weaker animal's threshold is lower than the stronger animal's threshold (Figure \ref{2dflex}).

@@

\begin{figure}
\includegraphics[width=\textwidth]{2d_accuracy.pdf}
\caption{\label{2dacc} }
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{2d_flexible_thresholds.pdf}
\caption{\label{2dflex} When the two thresholds in the two-dimensional case are allowed to vary freely, the decision process can be arbitrarily accurate in a given amount of time, depending on how much lower the weaker animal's threshold is than the stronger animal's threshold.  The expected time to reach a decision is on the x-axis and the probability of reaching the correct decision in that amount of time is on the y-axis.  The curve depends on the ratio of the weaker animal's threshold to the stronger animal's threshold ($\rho$).  Lower ratios are represented in higher darker curves.}
\end{figure}
